02_DESeq_characterization

### 2019-05-20 analysis/03_DESeq2_characterization.Rmd
rename

---
title: "05_DESeq_manipulation"
output: md_document
---

@@

knitr::opts_chunk$set(fig.path = '../figures/manipulation/', cache = TRUE)
```

@@

```{r readfiles}
# import "colData" which contains sample information and "countData" which contains read counts
m.colData <- read.csv("../metadata/00_colData_manipluation.csv", header = T, row.names = 1)
m.countData <- read.csv("../results/00_countData_manipluation.csv", header = T, row.names = 1)
geneinfo <- read.csv("../metadata/00_geneinfo.csv", row.names = 1)

# set levels
m.colData$treatment <- factor(m.colData$treatment, levels = 
                              c("m.inc.d3",  "m.inc.d8",
                                "m.inc.d9", "m.inc.d17",
                                "prolong", "extend", "m.n2"))

m.colData$sextissue <- as.factor(paste(m.colData$sex, m.colData$tissue, sep = "_"))

m.colData$outcome <- ifelse(grepl("d3|d9|d17", m.colData$treatment), "end inc", 
                     ifelse(grepl("d8|n2", m.colData$treatment),"end hatch",
                     ifelse(grepl("prolong", m.colData$treatment),"prolong inc",
                     ifelse(grepl("extend", m.colData$treatment),"delay hatch", NA))))

m.colData$outcome <- factor(m.colData$outcome, levels = 
                              c("end inc",  "end hatch",
                                "prolong inc", "delay hatch"))
summary(m.colData[c(7,3,4,5,8,9)])
```

@@

```{r totalDEGs, eval = T}
#create list of groups for deseq contrasts
group1 <- c("m.inc.d3","m.inc.d8", "m.inc.d9", "m.inc.d17", "prolong","extend", "m.n2" ) 
group2 <- group1

a <- plottotalDEGs(dds.female_hypothalamus, "female hypothalamus")
b <- plottotalDEGs(dds.female_pituitary, "female pituitary")
c <- plottotalDEGs(dds.female_gonad, "female gonad")
d <- plottotalDEGs(dds.male_hypothalamus, "male hypothalamus")
e <- plottotalDEGs(dds.male_pituitary, "male pituitary")
f <- plottotalDEGs(dds.male_gondad, "male gonad")

>>>>

---
title: "02_DESeq_characterization"
output: md_document
---

@@

knitr::opts_chunk$set(fig.path = '../figures/characterizatio/', cache = TRUE)
```

@@

```{r readfiles}
# import "colData" which contains sample information and "countData" which contains read counts
m.colData <- read.csv("../metadata/00_colData_characterization.csv", header = T, row.names = 1)
m.countData <- read.csv("../results/00_countData_characterization.csv", header = T, row.names = 1)
geneinfo <- read.csv("../metadata/00_geneinfo.csv", row.names = 1)

# set levels
levels(m.colData$treatment)
m.colData$treatment <- factor(m.colData$treatment, levels = 
                              c("control",  "bldg", "lay", "inc.d3", "inc.d9", "inc.d17", "hatch", "n5", "n9"))

m.colData$sextissue <- as.factor(paste(m.colData$sex, m.colData$tissue, sep = "_"))
summary(m.colData[c(7,3,4,5,8)])
```

@@

```{r totalDEGs, eval = T}
#create list of groups for deseq contrasts
group1 <- c("control",  "bldg", "lay", "inc.d3", "inc.d9", "inc.d17", "hatch", "n5", "n9")
group2 <- group1

a <- plottotalDEGschar(dds.female_hypothalamus, "female hypothalamus")
b <- plottotalDEGschar(dds.female_pituitary, "female pituitary")
c <- plottotalDEGschar(dds.female_gonad, "female gonad")
d <- plottotalDEGschar(dds.male_hypothalamus, "male hypothalamus")
e <- plottotalDEGschar(dds.male_pituitary, "male pituitary")
f <- plottotalDEGschar(dds.male_gondad, "male gonad")
